N-dimensional Tic Tac Toe, and Adventure in Modules

### 2017-05-12 paper/paper.tex
More work on section 3 - I think I'm going to rework the last paragraph and then move on to later sections

  As we touched on before - the notion of a game is generalized in the
  \texttt{game.sml} file. This defines the modules to run a game.
  The general pattern for a game under our model consists of three purposely
  isolated pieces.
  These are \textit{State}, \textit{Actions}, and \textit{Agents}.
  These are then wrapped together with a functor. The idea is that any game
  consists of a state, a set of actions on that state, and an agents that take
  actions for a state. A specific implementation of a game would use the
  relationship between these three general pieces to define a runnable game.

  Our implementation of \textit{Tic-tac-toe} uses this game model to operate and
  is primarily defined within \texttt{tictactoe.sml}.
  Here we have two signatures - one that extends state (the \texttt{STATE}
  signature from \texttt{game.sml}) for \textit{Tic-tac-toe}
  called \texttt{TTTSTATE} and another that does the same with action called
  \texttt{TTTACTION} - we don't extend the \texttt{AGENT} signature specifically.

@@

  The functor \texttt{TttActionFn} (used by modules structures like
  \texttt{TttAction} and \texttt{Ttt3DAction}) takes a module that implements
  \texttt{TTTSTATE} and gives us a module implementing \texttt{TTTACTION}.

  The idea being that we created specific modules structures
  (like \texttt{TttState}) for different
  cases of actions and states that may occur in various kinds of
  \textit{Tic-tac-toe} games. We then described functors
  which linked these structures to the functions meant for that specific use.
  When provided with the correct input module these functors will give us
  modules that implement that portion of the game pattern - which we then use
  with another structure and another functor for the next modular piece of the
  game.
  % ugh I should probably rewrite that last paragraph

>>>>

  As we touched on before - the notion of a game is generalized in the
  \texttt{game.sml} file. This defines the signatures and functor to run a game.
  The general pattern for a game under our model consists of three purposely
  isolated pieces.
  These are \textit{State}, \textit{Actions}, and \textit{Agents} which are
  each given their own signature in \texttt{game.sml}.
  These are then wrapped together with a functor. The idea is that any game
  consists of a state, a set of actions on that state, and an agents that take
  actions for a state. A specific implementation of a game would use the
  relationship between these three general pieces to define a runnable game with
  its own modules.

  Our implementation of \textit{Tic-tac-toe} uses this game model to operate and
  is primarily defined within \texttt{tictactoe.sml}.
  Here we have two signatures - one that extends state (the \texttt{STATE}
  signature from \texttt{game.sml}) for \textit{Tic-tac-toe}
  called \texttt{TTTSTATE} and another that does the same with action called
  \texttt{TTTACTION} - we don't extend the \texttt{AGENT} signature specifically
  for \textit{Tic-tac-toe}.

@@

  The functor \texttt{TttActionFn} (used by modules structures like
  \texttt{TttAction} and \texttt{Ttt3DAction}) takes a module that implements
  \texttt{TTTSTATE} and gives us a module implementing \texttt{TTTACTION}.
  The functors \texttt{TttRandomAgent} and \texttt{TttHumanAgentFn} take
  modules which implement \texttt{TTTACTION} and return a module that implements
  \texttt{AGENT}.

  We can then instantiate a structure like \texttt{TttExecRandom} that will run
  a game of \textit{Tic-tac-toe} by providing our \texttt{ExecFn} functor from
  \texttt{game.sml} with a module that implements \texttt{AGENT}.
  \texttt{ExecFn} then gives us a module that implements \texttt{EXEC}.

  The idea being that we instantiated specific module structures
  (like \texttt{TttState}) for different cases of actions and states that may
  occur in various kinds of \textit{Tic-tac-toe} games.
  We then described functors which linked these structures to the functions
  meant for that specific use and returned a new .
  When provided with the correct input module these functors will give us
  modules that implement that portion of the game pattern - which we then use
  with another structure and another functor for the next modular piece of the
  game.
  % ugh I should probably rewrite that last paragraph
